Capital Budget Funding in Toronto

### 2024-09-27 paper/paper.qmd
fixed wording for education results

Educational attainment appears to have a strong positive relationship with funding allocations. Wards where a higher percentage of residents hold a bachelor's degree or higher tend to receive more per capita funding. A higher percentage of residents holding a bachelor's degree or higher is defined as a 33%. Notable examples include:

-   **Ward 10**, where **60.97%** of residents have at least a bachelor's degree, receives **\$4,127.10** per capita, the second highest per capita funding.
-   **Ward 11**, with **56.07%** of residents holding a bachelor's degree or higher, receives **\$1,637.81** per capita.
-   Conversely, **Ward 7**, with only **14.67%** educational attainment at this level, receives **\$852.05** per capita.

**Figure 3** shows a clear upward trend, indicating that higher educational attainment within a ward is associated with increased capital funding per capita.

```{r Figure 4, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-education

@@

>>>>

We will also classify wards where at least 33% of residents hold a bachelor's degree or higher as having high educational attainment. There is a clear positive relationship between educational attainment and per capita funding as wards with higher education levels tend to receive more funding. More specifically, Ward 10, with 60.97% of residents holding a bachelor’s degree, received \$4,127.10 per capita, while Ward 11, with 56.07%, received \$1,637.81 per capita. In contrast, Ward 7, where only 14.67% of residents hold a degree, received just \$852.05 per capita.

```{r Figure 4, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-education
#| fig-cap: Scatter plot illustrating the relationship between Per Capita Funding and Education Levels

@@

The trend line in @fig-education illustrates that, generally, wards with a higher percentage of degree holders are more likely to see higher per capita funding allocations. Ward 13 was excluded from this analysis due to its skewing effect on the data.
